Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Remove quotation marks

Essentially, each of these system uses some mechanism to ``shuffle'' votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

>>>>

Essentially, each of these system uses some mechanism to shuffle votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.
